Four reasons your build is slow

### 2019-01-17 paper.tex
to merge

Google's protocol buffers project \cite{protobufs3.6.1} exhibited this behavior.  It's work was calculated
to be about 16.7 minutes and it had a relatively
long predicted span of 43.7 seconds, which was dominated by a call to g++ compiling
a single file.  When the analysis applied in section \ref{sec:expensive} is applied to
protocol buffers' build, we learn that if the code in fig. \ref{code:g++1} wasn't part of the span,
the new span would be about 31s and would be dominated by the code in fig. \ref{code:g++2}.
And when that
code isn't part of the span, we learn that the new span is again dominated by another
g++ call in the code in fig. \ref{g++3}.  If none of these g++ compilations are in the span,
the new span of the project is about 20s, roughtly half of the original span.

@@

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  g++ \$(FLAGS)
  -o google/protobuf/descriptor.lo
  google/protobuf/descriptor.cc
\end{Verbatim}
\caption{A simplification of the real command run by make; compiles a single file and took about
40 seconds to run and was 90\% of the span.}
\label{code:g++1}
\end{figure}

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  g++ \$(FLAGS)
  -o google/protobuf/descriptor.pb.lo
  google/protobuf/descriptor.pb.cc
\end{Verbatim}
\caption{A simplification of the real command run by make; compiles a single file and took about
27 seconds to run and was about 87\% of the span.}
\label{code:g++2}
\end{figure}

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  g++ \$(FLAGS)
  -o google/protobuf/compiler/cpp/cpp\_message.lo
  google/protobuf/compiler/cpp/cpp\_message.cc
\end{Verbatim}
\caption{A simplification of the real command run by make; compiles a single file and took about
22.5 seconds to run and was about 90\% of the span.}
\label{code:g++3}
\end{figure}

>>>>

Google's protocol buffers project \cite{protobufs3.6.1} exhibited this behavior.  It's work was calculated
to be about 16.7 minutes and it had a relatively
long predicted span of 43.7 seconds, which was dominated by a call to g++ compiling
a single file.  When the analysis applied in section \ref{sec:expensive} is applied to
protocol buffers' build, we learn that if the code, a simplification of the real code,
in fig. \ref{code:g++1} wasn't part of the span,
the new span would be about 31s and would be dominated by the code in fig. \ref{code:g++2}, also
a simplification.
And when that
code isn't part of the span, we learn that the new span is again dominated by another
g++ call in the code in fig. \ref{g++3}, also a simplification.
If none of these g++ compilations are in the span,
the new span of the project is about 20s, roughtly half of the original span.

@@

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  g++ \$(FLAGS)
  -o google/protobuf/descriptor.lo
  google/protobuf/descriptor.cc
\end{Verbatim}
\caption{Compiles a single file and took about 40 seconds to run and was 90\% of the span.}
\label{code:g++1}
\end{figure}

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  g++ \$(FLAGS)
  -o google/protobuf/descriptor.pb.lo
  google/protobuf/descriptor.pb.cc
\end{Verbatim}
\caption{Compiles a single file and took about 27 seconds to run and was about 87\% of the span.}
\label{code:g++2}
\end{figure}

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  g++ \$(FLAGS)
  -o google/protobuf/compiler/cpp/cpp\_message.lo
  google/protobuf/compiler/cpp/cpp\_message.cc
\end{Verbatim}
\caption{Compiles a single file and took about 22.5 seconds to run and was about 90\% of the span.}
\label{code:g++3}
\end{figure}
